\EVOSUITE at the SBST 2019 Tool Competition

### 2019-03-27 papers/sbst19/paper_sbst19.tex
Few minor changes

\EVOSUITE can be configured to satisfy for multiple coverage criteria at the same time, and the default configuration combines branch coverage with
mutation testing~\cite{emse14_mutation} and other basic
criteria~\cite{rojas2015combining}. Once the search is completed, \EVOSUITE applies various post-search optimizations aimed to improve the readability of
the generated tests. For example, tests are minimized and test assertions are selected using mutation analysis~\cite{10.1109/TSE.2011.93}. For more details on post-process optimization we refer to~\cite{FrA11c,FrA13a}.

@@

The configuration of \EVOSUITE for the 2019 competition is largely
based on its default values, since these have been tuned
extensively~\cite{arcuri2013parameter}. We used the default set of
coverage criteria~\cite{rojas2015combining} (e.g., line coverage,
branch coverage, branch coverage by direct method invocation, weak
mutation testing, output coverage, exception coverage). \EVOSUITE uses
an archive of solutions~\cite{emse_archive} to keep the search focused
on uncovered goals, iteratively discarding covered goals and storing
the tests that covered them. After a certain percentage of the search
budget has passed and with a certain probability, \EVOSUITE starts
using mock objects (relying on Mockito) instead of actual class
instances~\cite{ICST_Mocking17} for dependencies; only branches that
cannot be covered without mocks lead to tests with mock objects. As in
the previous instance of the competition, we continue to use
frequency-based weighted constants for
seeding~\cite{sakti2015instance} and support Java Enterprise Edition
features~\cite{arcuri2016java}. %\TODO{any other noteworthy change?} No.
\EVOSUITE is actively maintained, therefore several bug fixes and
minor improvements have been applied since the last instance of the
competition, in particular in relation to non-determinism and flaky
tests~\cite{arcuri2014automated}, as well as new types of test
assertions (e.g., related to arrays and standard container classes).

@@

A closer look at the benchmarks DUBBO-2 and WEBMAGIC-4 reveals that
there were missing dependencies in the competition
setup~\cite{sbst19competition} (similar to cases in previous
years~\cite{evosuiteAtSbst2018}), which explains why \EVOSUITE was
incapable of generating any test: When a dependency of the class
under test is missing, then \EVOSUITE intentionally aborts with an
error to inform the user of the configuration error. While this is
desirable behavior during regular usage, arguably in the scope of the
competition \EVOSUITE could try to ignore such errors and try to
generate tests nevertheless, as it might still be possible to cover
code even with some missing dependencies. For the benchmark
FASTJSON-3 and a 10s time budget, \EVOSUITE generated some test
suites but due to a bug in the
competition infrastructure, no data was collected. % FileNotFoundException in the infrastructure

For the benchmarks SPOON-169 and SPOON-25, \EVOSUITE either failed to generated
a compilable test suite or crashed due to a bug in DynaMOSA. Although \EVOSUITE's
minimization could help at reducing the number of uncompilable / flaky test cases,
for SPOON-169 all minimizations attempts ran out of time.
% SPOON-169
% Minimization timeout. Roll back to original test suite
% and therefore the test suite

For the AUTHZFORCE benchmarks, although \EVOSUITE managed to generate
some test suites, most executions for data collection ended with a
failure. Specifically, for these classes an exception was raised for
test execution for \emph{all} tools in the competition. However,
while this exception was not problematic for other tools, it caused
an inconsistent state of the JVM which led to the \texttt{@Before}
setup methods of \EVOSUITE to fail (the \texttt{@Before} method was
not able to configure \EVOSUITE's custom security manager because it
was never correctly removed). As a consequence, all test executions
failed. We were not able to reproduce the error in the competition
infrastructure, and thus cannot conjecture about the causes. The same
problem also occurred for SPOON-253. While in principle it would be
possible to extend \EVOSUITE to try to ignore such errors and keep on
executing tests, as explained it is \EVOSUITE's philosophy that the
user should be made aware of configuration errors, and hence such an
extension would only serve to tune \EVOSUITE for the competition.

In general, \EVOSUITE often struggles with a time budget as low as 10
seconds. For example, Table~\ref{table:results} reports ``-'' for
benchmarks FASTJSON-1, FASTJSON-3, FESCAR-41, FESCAR-42, and
SPOON-105.
% last message in the log files was * Initial Number of Goals in DynMOSA = 942 / 10337
%\TODO{either infinite loop, took much time to start evolving, or DynaMOSA can't
%be used in this benchmarks with a time budget of 10s.}
%
Surprisingly, for benchmarks SPOON-155, SPOON-16, SPOON-20, and
SPOON-211, \EVOSUITE successfully generated test suites for small
time budgets but it failed to do it for large time budgets. For all,
\EVOSUITE crashed due to a bug in the DynaMOSA algorithm which had
not been revealed by our previous experiments. Consequently, even
though DynaMOSA is known to increase the coverage \EVOSUITE achieves
subtantially in general, this increase was countered with some
missing datapoints. As always, the competition was helpful in
improving the robustness of the tool, by revealing this and other
bugs.
%% SPOON-155 (240s), SPOON-16 (120s), SPOON-20 (120s and 240s), SPOON-211 (120s)
%java.lang.NullPointerException: null
%	at org.evosuite.ga.operators.ranking.RankBasedPreferenceSorting.getNumberOfSubfronts(RankBasedPreferenceSorting.java:158) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]
%	at org.evosuite.ga.metaheuristics.mosa.DynaMOSA.generateSolution(DynaMOSA.java:152) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]
%	at org.evosuite.strategy.MOSuiteStrategy.generateTests(MOSuiteStrategy.java:115) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]

>>>>

\EVOSUITE can be configured to satisfy for multiple coverage criteria at the same time, and the default configuration combines branch coverage with
mutation testing~\cite{emse14_mutation} and other basic
criteria~\cite{rojas2015combining}. Once the search is completed, \EVOSUITE applies various post-search optimisations aimed to improve the readability of
the generated tests. For example, tests are minimised and test assertions are selected using mutation analysis~\cite{10.1109/TSE.2011.93}. For more details on post-process optimisation we refer to~\cite{FrA11c,FrA13a}.

@@

The configuration of \EVOSUITE for the 2019 competition is largely
based on its default values since these have been tuned
extensively~\cite{arcuri2013parameter}. We used the default set of
coverage criteria~\cite{rojas2015combining} (e.g., line coverage,
branch coverage, branch coverage by direct method invocations, weak
mutation testing, output coverage, exception coverage). \EVOSUITE uses
an archive of solutions~\cite{emse_archive} to keep the search focused
on uncovered goals, iteratively discarding covered goals and storing
the tests that covered them. After a certain percentage of the search
budget has passed and with a certain probability, \EVOSUITE starts
using mock objects (relying on Mockito) instead of actual class
instances~\cite{ICST_Mocking17} for dependencies; only branches that
cannot be covered without mocks lead to tests with mock objects. As in
the previous instance of the competition, we continue to use
frequency-based weighted constants for
seeding~\cite{sakti2015instance} and support Java Enterprise Edition
features~\cite{arcuri2016java}. %\TODO{any other noteworthy change?} No.
\EVOSUITE is actively maintained, therefore several bug fixes and
minor improvements have been applied since the last instance of the
competition, in particular regarging non-determinism and flaky
tests~\cite{arcuri2014automated}, as well as new types of test
assertions (e.g., related to arrays and standard container classes).

@@

A closer look at the benchmarks DUBBO-2 and WEBMAGIC-4 reveals that
there were missing dependencies in the competition
setup~\cite{sbst19competition} (similar to cases in previous
years~\cite{evosuiteAtSbst2018}), which explains why \EVOSUITE was
incapable of generating any test: When a dependency of the class
under test is missing, then \EVOSUITE intentionally aborts with an
error to inform the user of the configuration error. While this is
desirable behavior during regular usage, arguably in the scope of the
competition, \EVOSUITE could try to ignore such errors and try to
generate tests nevertheless, as it might still be possible to cover
code even with some missing dependencies. For the benchmark
FASTJSON-3 and a 10s time budget, \EVOSUITE generated some test
suites, but due to a bug in the
competition infrastructure, no data was collected. % FileNotFoundException in the infrastructure

For the benchmarks SPOON-169 and SPOON-25, \EVOSUITE either failed to generate
a compilable test suite or crashed due to a bug in DynaMOSA. Although \EVOSUITE's
minimization could help at reducing the number of uncompilable / flaky test cases,
for SPOON-169 all minimizations attempts ran out of time.
% SPOON-169
% Minimization timeout. Roll back to original test suite
% and therefore the test suite

For the AUTHZFORCE benchmarks, although \EVOSUITE managed to generate
some test suites, most executions for data collection ended with a
failure. Specifically, for these classes, an exception was raised for
test execution for \emph{all} tools in the competition. However,
while this exception was not problematic for other tools, it caused
an inconsistent state of the JVM which led to the \texttt{@Before}
setup methods of \EVOSUITE to fail (the \texttt{@Before} method was
not able to configure \EVOSUITE's custom security manager because it
was never correctly removed). As a consequence, all test executions
failed. We were not able to reproduce the error in the competition
infrastructure, and thus cannot conjecture about the causes. The same
problem also occurred for SPOON-253. While in principle it would be
possible to extend \EVOSUITE to try to ignore such errors and keep on
executing tests, as explained it is \EVOSUITE's philosophy that the
user should be made aware of configuration errors, and hence such an
extension would only serve to tune \EVOSUITE for the competition.

In general, \EVOSUITE often struggles with a time budget as low as 10
seconds. For example, Table~\ref{table:results} reports ``-'' for
benchmarks FASTJSON-1, FASTJSON-3, FESCAR-41, FESCAR-42, and
SPOON-105.
% last message in the log files was * Initial Number of Goals in DynMOSA = 942 / 10337
%\TODO{either infinite loop, took much time to start evolving, or DynaMOSA can't
%be used in this benchmarks with a time budget of 10s.}
%
Surprisingly, for benchmarks SPOON-155, SPOON-16, SPOON-20, and
SPOON-211, \EVOSUITE successfully generated test suites for small-time 
budgets, but it failed to do it for large time budgets. For all,
\EVOSUITE crashed due to a bug in the DynaMOSA algorithm which had
not been revealed by our previous experiments. Consequently, even
though DynaMOSA is known to increase the coverage, \EVOSUITE achieves
substantially in general, this increase was countered with some
missing datapoints. As always, the competition was helpful in
improving the robustness of the tool, by revealing this and other
bugs.
%% SPOON-155 (240s), SPOON-16 (120s), SPOON-20 (120s and 240s), SPOON-211 (120s)
%java.lang.NullPointerException: null
%	at org.evosuite.ga.operators.ranking.RankBasedPreferenceSorting.getNumberOfSubfronts(RankBasedPreferenceSorting.java:158) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]
%	at org.evosuite.ga.metaheuristics.mosa.DynaMOSA.generateSolution(DynaMOSA.java:152) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]
%	at org.evosuite.strategy.MOSuiteStrategy.generateTests(MOSuiteStrategy.java:115) ~[evosuite-master-1.0.7-SNAPSHOT.jar:1.0.7-SNAPSHOT]
